### 2020-04-23 README.Rmd
readme fsize
typos

### Overview

The package `covid19census` provides functions to extract COVID-19 cases, deaths, hospitalizations and test of U.S. and Italy at the county and regional level, respectively, and then combine them with other population metric (age, sex, prevalence of chronic conditions, income indexes, access to health services and many others.)

### Installation

@@

### Usage

@@

### U.S. Datasets and Sources

@@

### Italy: Datasets and Sources

@@

### Raw Data and other Scripts

@@

### Terms of Use

>>>>

## Overview

The package `covid19census` provides functions to extract COVID-19 cases, deaths, hospitalizations and test of U.S. and Italy at the county and regional level, respectively, and then combine them with other population metrics (age, sex, prevalence of chronic conditions, income indexes, access to health services and many others.)

## Installation

@@

## Usage

@@

## U.S. Datasets and Sources

@@

## Italy: Datasets and Sources

@@

## Raw Data and other Scripts

@@

## Terms of Use
